Measuring contrast processing in the visual system using SSVEP

### 2024-04-06 review.qmd
Added amblyopia section

---
title: "Measuring contrast processing in the visual system using SSVEP"
author:
  - name: Alex R. Wade
  - name: Daniel H. Baker
format: 
  pdf:
    keep-tex: true
bibliography: WadeBaker_Review.bib
csl: visual-neuroscience.csl
execute:
  echo: false
---
<p style="text-align: center;">Department of Psychology and York Biomedical Research Institute

University of York, UK</p>

@@

Amblyopia

>>>>

---
title: "Measuring contrast processing in the visual system using SSVEP"
author:
  - name: Alex R. Wade
  - name: Daniel H. Baker
format: 
  pdf:
    keep-tex: true
bibliography: WadeBaker_Review.bib
csl: visual-neuroscience.csl
execute:
  echo: false
---
Department of Psychology and York Biomedical Research Institute, University of York, UK

@@

Amblyopia is a disorder of binocular vision, characterised by one eye contributing much less to perception than the other. This is often due to strabismus (squint) or anisometropia (difference in optical prescription between the eyes) during development. Contemporary accounts suggest that the amblyopic eye is suppressed by signals from the fellow eye. SSVEPs provide a convenient and objective method to characterise the difference in neural response to signals in each eye, and typically show reduced responses to stimuli in the amblyopic eye across the contrast range [@Baker2015]. There are currently many novel binocular treatments for amblyopia under development, often involving virtual reality or stereo display systems designed to encourage the two eyes to work together. The steady-state approach may be more sensitive and objective than typical acuity measurements, and also has the potential to measure suppression between the eyes directly [e.g. @Zheng2019; @Du2023; @Hu2023].
